A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage

### 2024-06-03 paper/main.tex
sec4.2, discussion

Logic states coalesce the program behaviors in a fewer logic states as the
behaviors contain more branch repetitions, resulting in a smaller (larger)
logic state coverage as it observes more uninteresting (interesting) program
behaviors.

>>>>

Logic states coalesce the program behaviors in a fewer logic states as the
behaviors contain more branch repetitions, resulting in smaller (larger)
logic state coverage as it observes more uninteresting (interesting) program
behaviors.
